Deliminative verbal reduplication in Mandarin Chinese

### 2024-08-23 chapters/ch04-Previous.tex
Update 2024-08-23-17:36:32

Previous analyses on the reduplication in Mandarin Chinese and in other languages can be classified
into three groups:  the reduplication as a verbal classifier phrase (\sectref{sec:clf}), as an aspect marker (\sectref{sec:asp}), and
as a special reduplication construction (\sectref{sec:construc}).\footnote{The term \textit{construction} is used here in its general sense, not in the sense of Construction Grammar.} 
This section will review these analyses and will discuss their advantages and shortcomings.

@@

\citet{Fan1964}, \citet[205]{Chao1968} and \citet{Xiong2016} analyzed the reduplication in Mandarin Chinese
as a verbal classifier phrase\footnote{Alternative terms for \textit{verbal classifier}: \textit{measure for verbs of action} in \citet[615]{Chao1968} or \textit{cognate object} in \citet[312]{Chao1968} and  \citet[263]{Hong1999}.
The \textit{verbal classifier phrase}  is also termed \textit{quantity adverbial} in \citet[352--353]{LiThompson1981} or \textit{frequency phrase} in \citet[91]{Huangetal2009}.}.
A verbal classifier is ``a measure for verbs of action expresses the number of times an action takes place” \citep[615]{Chao1968}, such as the \textit{ci} in (\ref{ex:clf}).

%\settowidth\jamwidth{(Chomsky, 1957: 15)}
\ea\label{ex:clf}
\gll mei che guo yi ci huang\\
not tell \textsc{exp} one \textsc{clf} lie\\ \hfill {\citep[616]{Chao1968}}
\glt `haven't told lie once'
\z

In this analysis, the first element in the reduplication is the actual verb, 
the second element is a verbal classifier borrowed from a verb, 
and \textit{yi} `one' is an optional pseudo-numeral that only has an abstract `a little bit' meaning.
The analysis is syntactic.

The parallel between the reduplication and a verbal classifier phrase is obvious. 
Both the reduplication and the verbal classifier phrase serve to quantify the duration or the extent of a situation. 
A reduplication structure can often be paraphrased into a verbal classifier phrase such as \textit{yi xia} ‘once, a while’, \textit{yi hui} ‘a while’, as illustrated in (\ref{ex:redup-clf}).

\ea\label{ex:redup-clf}
	\ea \gll \textit{deng}-\textit{deng} wo.\\
		wait-wait I\\
		\glt `Wait for me a little bit.'
	\ex \gll deng wo yi xia.\\
	wait I one \textsc{clf}\\
	\glt `Wait for me a little while.'
	\z
\z

However, there are several arguments suggesting that the reduplication cannot be analyzed the same way as a verbal classifier phrase. First, the verb and the verbal classifier can be separated (\ref{ex:clf-sep}), while the reduplication cannot (\ref{ex:redup-sep}) \citep[269]{Paris2013}.

\ea\label{ex:clf-sep}
  \ea \gll ni deng yi xia Zhangsan!\\
   you wait one \textsc{clf} Zhangsan\\
   \glt `Wait for Zhangsan for a while!'
  \ex \gll ni deng Zhangsan yi xia!\\
   you wait Zhangsan one \textsc{clf}\\
   \glt `Wait for Zhangsan for a while!'
\z
\z

\ea\label{ex:redup-sep}
  \ea[]{\gll ni \textit{deng}-\textit{yi}-\textit{deng} Zhangsan!\\
   you wait-one-wait Zhangsan\\
   \glt `Wait for Zhangsan a little bit!'}
  \ex[*]{\gll ni \textit{deng} Zhangsan \textit{yi} \textit{deng}!\\
  you wait Zhangsan one wait\\}
\z
\z

Second, unlike verbal classifiers (\ref{ex:clf-num}), the \textit{yi} ‘one’ in A-\textit{yi}-A cannot be replaced by other numerals (\ref{ex:redup-num}) \citep[299--230]{YangWei2017}.

\ea\label{ex:clf-num}
  \ea \gll ta pai-le wo yi xia.\\
   he pat-\textsc{pfv} I one \textsc{clf}\\
   \glt `He patted me once.'
   \ex \gll ta pai-le wo liang xia.\\
    he pat-\textsc{pfv} I two \textsc{clf}\\
    \glt `He patted me twice.'
\z
\z

\ea\label{ex:redup-num}
  \ea[]{\gll ta \textit{pai}-\textit{le}-\textit{yi}-\textit{pai} wo.\\
   he pat-\textsc{pfv}-one-pat I\\
   \glt `He patted me a little bit.'}
   \ex[*]{\gll ta \textit{pai}-\textit{le}-\textit{liang}-\textit{pai} wo.\\
   he pat-\textsc{pfv}-two-pat I\\}
\z
\z

Third, idioms (\ref{ex:idiom}) lose their idiomatic meaning when used with verbal classifiers (\ref{ex:clf-idiom}), but maintain their idiomatic meaning with reduplications (\ref{ex:redup-idiom}) \citep[230--231]{YangWei2017}.

\ea
  \ea\label{ex:idiom}
  \gll bao fo-jiao\\
  clasp Buddha-foot\\
   \glt Literal: `clasp the Buddha's foot'\\
   Idiomatic: `make a last-minute effort'

   \ex\label{ex:clf-idiom}
   \gll ta kaoshi qian bao-le san xia fo-jiao.\\
   he exam before clasp-\textsc{pfv} three \textsc{clf} Buddha-foot\\
   \glt `He clasped the Buddha's foot three times before the exam.' (idiomatic reading unavailable)

   \ex\label{ex:redup-idiom}
   \gll ta kaoshi qian \textit{bao}-\textit{le}-\textit{bao} fo-jiao.\\
   he exam before clasp-\textsc{pfv}-clasp Buddha-foot\\
   \glt Literal: `He clasped the Buddha's foot a little bit before the exam.'\\
   Idiomatic: `He made a bit of a last-minute effort before the exam.'
\z
\z

@@

%%%%%%%%%%%
\subsection{The reduplicant as an aspect marker}\label{sec:asp}

A number of studies consider the reduplication to be a delimitative aspect marker \citep{Arcodiaetal2014, BascianoMelloni2017, YangWei2017} 
due to its delimitative aspectual meaning. 
\citet{Travis1999, Travis2000} also analyzed the reduplication in Tagalog as an imperfective aspect marker.

@@

 \citet{Arcodiaetal2014} and \citet{BascianoMelloni2017} analyzed the reduplication within the
framework of First Phase Syntax \citep{Ramchand2008}.
\citet{Ramchand2008} proposed that an event is comprised of the following phrases: 
the causative subevent (\textit{init}P), the process subevent (\textit{proc}P) and the result subevent (\textit{res}P), which are ordered hierarchically, as illustrated in \figref{tree:ramchand}.\footnote{
The present study does not argue for a {NP} or a {DP} analysis and simply takes over the illustration provided in the cited papers.}
Dynamic and volitional verbs have the features [init proc] and are therefore located under \textit{init} and \textit{proc}  \citetext{\citealp[24]{Arcodiaetal2014}; \citealp[147]{BascianoMelloni2017}}.  
Achievement verbs possess the feature [res] and reside under \textit{res}  \citetext{\citealp[24]{Arcodiaetal2014}; \citealp[147]{BascianoMelloni2017}}. 
Stative verbs do not contain a \textit{proc}P \citep[152]{BascianoMelloni2017}.

@@

\citet{Arcodiaetal2014} and \citet{BascianoMelloni2017} assumed that the first element in the reduplication is the actual verb, which resides under \textit{init} and \textit{proc}, 
and that the second element is an aspect marker, which resides in the complement position of \textit{proc}, as it delimits the process of the event. 
Since the second element occupies the same syntactic position as \textit{res}P, it should have complementary distribution with \textit{res}P
and should thus be incompatible with achievement verbs because of their [res] feature.
Furthermore, if \textit{proc}P does not exist in the event, as in the case of states, there should be no place for the reduplication either.

@@

 \citet[229]{YangWei2017} endorsed the analysis of  reduplication as an aspect marker following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.
 \citet{Tsai2008} provided the syntactic analysis for aspect markers in Mandarin Chinese as shown in \figref{tree:tsai}.\footnote{Asp = Aspect}
He observed that  \textit{zhe} `\textsc{prog}', \textit{le} `\textsc{pfv}' and \textit{wan} `\textsc{compl}' necessarily occur with additional information about the event denoted by the sentence (\ref{ex:incomplete}), 
while \textit{zai} `\textsc{dur}' and \textit{guo} `\textsc{exp}' can occur without further information (\ref{ex:complete}).

\ea\label{ex:incomplete}
 \gll Xiaoli chi-zhe/le/wan fan *(le).\\
 Xiaoli eat-\textsc{prog}/\textsc{pfv}/\textsc{compl} meal \textsc{ptc}\\
 \glt `Xiaoli is eating/ate/finished eating the meal.'
\z

\ea\label{ex:complete}
\gll Xiaoli (gangcai) zai ku/ku-guo.\\
Xiaoli just.now \textsc{dur} cry/cry-\textsc{exp}\\
\glt `Xiaoli was crying/cried just now.'
\z
He thus proposed three aspect positions under TP. \textit{zai} and \textit{guo} reside under Asp$_1$, while \textit{zhe} and \textit{le} under Asp$_2$, as illustrated in \figref{tree:tsai}.\footnote{\citet{Tsai2008} differentiated the middle and the inner aspect based on the fact that \textit{wan} can only occur with certain types of predicate. This differentiation does not play a role for our purpose and will not be further discussed here.}

@@

\ea\label{ex:redup-tsai}
\ea[*] {\gll ta \textit{xiao}-\textit{xiao}\\
he laugh-laugh\\}
\ex[] {\gll ta \textit{xiao}-\textit{le}-\textit{xiao}\\
he laugh-\textsc{pfv}-laugh\\
\glt `He laughed a little.'}
\ex[] {\gll ta \textit{xiao}-\textit{xiao}, bu shuohua\\
he laugh-laugh not speak\\
\glt `He laughed a little, and didn't speak.'}\label{ex:redup-tsai-co}
\z
\z

@@

This analysis would result in a mismatch between syntax and semantics. 
Even though \textit{le}, \textit{guo} and reduplication all mark perfective aspects (\sectref{sec:aspM}, \citealt{Dai1997, XiaoMcEnery2004}),
\textit{guo} is situated under Asp$_1$ while \textit{le} and the reduplication are under Asp$_2$, as can be seen from \figref{tree:redupasp}.

In sum, both analyses of the reduplicant as an aspect marker do not seem to be convincing.

@@

The following section discusses previous literature which proposed a special construction for the reduplication.

@@

\citet*{FanSongBond2015} provided a unified HPSG analysis for the reduplication of both verbs and adjectives in Mandarin Chinese.
They considered reduplication to be a morphological process and modeled it via lexical rules.
They provided the lexical rule (\ref{avm:fsb-redup}) for reduplication in general,
and further proposed \type{redup-a-lr} and \type{redup-v-lr} as subtypes of \type{redup-type}, 
as illustrated in (\ref{avm:fsb-redup-a}) and (\ref{avm:fsb-redup-v}) respectively.\footnote{%
  Note that the format in which the lexical rule is given is not the input--output format usually
  used for lexical rules in HPSG. Instead it is depicted as a unary branching phrase structure
  rule: the input is the daughter on the right-hand side of the rule. The output is the mother on
  the left-hand side. The view of lexical rules as unary branching rules is adopted in most current work on
  lexical rules \citep{BC99a,Meurers2001a} despite the notation that is commonly assumed.  
}
For them, the reduplication functions as an intensifier predicate, as represented in the \textsc{predicate (pred)} in the \textsc{constructional-content (c-cont)}.
The \type{intensifier\_x\_rel} has two subtypes: \type{redup\_up\_x\_rel} for the amplifiying meaning of adjectival reduplication and \type{redup\_down\_x\_rel} for the delimitative meaning of verbal reduplication.
The orthography is handled separately.
The AABB form for adjectives and the ABAB form for verbs, as well as the AAB form for V-O compounds, are handled as irregular derivation forms.

@@

This approach provided a unified account for adjectival and verbal reduplication.
Their commonalities are captured by inheritance hierarchies of the intensifier predicates and the lexical rules.
In the case of verbal reduplication, A-\textit{yi}-A is analyzed as an alternative orthographical form of AA.
This correctly captured the intuition that AA and A-\textit{yi}-A express the same meaning and only differ from each other phonologically/orthographically (see \sectref{sec:core-sem}).

>>>>

Previous analyses on the reduplication in Mandarin Chinese and in other languages can be classified
into three groups:  the reduplication as a verbal classifier phrase (\sectref{sec:clf}), as an aspect modifier (\sectref{sec:asp}), and
as a special reduplication construction (\sectref{sec:construc}).\footnote{The term \textit{construction} is used here in its general sense, not in the sense of Construction Grammar.} 
This section will review these analyses and will discuss their advantages and shortcomings.

@@

\citet{Fan1964}, \citet[205]{Chao1968} and \citet{Xiong2016} analyze the reduplication in Mandarin Chinese
as a verbal classifier phrase\footnote{Alternative terms for \textit{verbal classifier}: \textit{measure for verbs of action} in \citet[615]{Chao1968} or \textit{cognate object} in \citet[312]{Chao1968} and  \citet[263]{Hong1999}.
The \textit{verbal classifier phrase}  is also termed \textit{quantity adverbial} in \citet[352--353]{LiThompson1981} or \textit{frequency phrase} in \citet[91]{Huangetal2009}.}.
A verbal classifier is ``a measure for verbs of action expresses the number of times an action takes place” \citep[615]{Chao1968}, such as the \obj{ci4} in (\ref{ex:clf}).

%\settowidth\jamwidth{(Chomsky, 1957: 15)}
\ea\label{ex:clf}
\gll \objex{mei2} \objex{che3} \objex{guo4} \objex{yi2} \objex{ci4} \objex{huang3}\\
not tell \textsc{exp} one \textsc{clf} lie\\ \hfill {\citep[616]{Chao1968}}
\glt `haven't told lie once'
\z

In this analysis, the first element in the reduplication is the actual verb, 
the second element is a verbal classifier borrowed from a verb, 
and \obj{yi} `one' is an optional pseudo-numeral that only has an abstract `a little bit' meaning.
The analysis is syntactic.

The parallel between the reduplication and a verbal classifier phrase is obvious. 
Both the reduplication and the verbal classifier phrase serve to quantify the duration or the extent of a situation. 
A reduplication structure can often be paraphrased into a verbal classifier phrase such as \obj{yi2} \obj{xia4} ‘once, a while’, \obj{yi2} \obj{hui4} ‘a while’, as illustrated in (\ref{ex:redup-clf}).

\ea\label{ex:redup-clf}
	\ea \gll \obj{deng3}-\obj{deng3} \objex{wo3}.\\
		wait-wait I\\
		\glt `Wait for me a little bit.'
	\ex \gll \objex{deng3} \objex{wo3} \objex{yi2} \objex{xia4}.\\
	wait I one \textsc{clf}\\
	\glt `Wait for me a little while.'
	\z
\z

However, there are several arguments suggesting that the reduplication cannot be analyzed the same way as a verbal classifier phrase. First, the verb and the verbal classifier can be separated (\ref{ex:clf-sep}), while the reduplication cannot (\ref{ex:redup-sep}) \citep[269]{Paris2013}.\footnote{
One reviewer notes that the objects that can be placed in between the verbal classifier phrase is usually limited to pronouns and proper nouns.
We found some examples from the corpus showing that not only pronouns and proper nouns can be placed before \obj{yi2} \obj{xia4} `once':
\ea%她看了他的脸一下。(CCL)
\gll \objex{ta1} \objex{kan4-le} \objex{ta1de} \objex{lian3} \objex{yi2} \objex{xia4}.\\
she look-\textsc{pfv} his face one time\\\jambox{(CCL)}
\glt `She took a look at his face.'

\ex%他没碰窗户，就看了玻璃一下，玻璃就烂了。(CCL)
\gll \objex{ta1} \ldots\, \objex{jiu4} \objex{kan4-le} \objex{bo1li} \objex{yi2} \objex{xia4}, \objex{bo1li} \objex{jiu4} \objex{lan4-le}.\\
he {} just look-\textsc{pfv} glass one time glass just break-\textsc{pfv}\\\jambox{(CCL)}
\glt `He just took a look at the glass and the glass just broke.'
\z
We think it has to do with the length of the object, i.e. shorter objects can be placed before  \obj{yi2} \obj{xia4} `once' while longer ones cannot.
%This is not necessarily a syntactic constraint

Even if we accept that the object can be only be placed before  \obj{yi2} \obj{xia4} `once' in limited cases,
the fact that the object can be placed before  \obj{yi2} \obj{xia4} `once' in some cases but in no cases in between reduplication suggests there is a fundamental difference between the structure of the two phenomena.
}

\ea\label{ex:clf-sep}
  \ea \gll \objex{ni3} \objex{deng3} \objex{yi2} \objex{xia4} \objex{Zhang1san1}!\\
   you wait one \textsc{clf} Zhangsan\\
   \glt `Wait for Zhangsan for a while!'
  \ex \gll \objex{ni3} \objex{deng3} \objex{Zhang1san1} \objex{yi2} \objex{xia4}!\\
   you wait Zhangsan one \textsc{clf}\\
   \glt `Wait for Zhangsan for a while!'
\z
\z

\ea\label{ex:redup-sep}
  \ea[]{\gll \objex{ni3} \obj{deng3}-\obj{yi}-\obj{deng3} \objex{Zhang1san1}!\\
   you wait-one-wait Zhangsan\\
   \glt `Wait for Zhangsan a little bit!'}
  \ex[*]{\gll \objex{ni3} \obj{deng3} \objex{Zhang1san1} \obj{yi} \obj{deng3}!\\
  you wait Zhangsan one wait\\}
\z
\z

Second, unlike verbal classifiers (\ref{ex:clf-num}), the \obj{yi} ‘one’ in A-\obj{yi}-A cannot be replaced by other numerals (\ref{ex:redup-num}) \citep[299--230]{YangWei2017}.

\ea\label{ex:clf-num}
  \ea \gll \objex{ta1} \objex{pai1}-le \objex{wo3} \objex{yi2} \objex{xia4}.\\
   he pat-\textsc{pfv} I one \textsc{clf}\\
   \glt `He patted me once.'
   \ex \gll \objex{ta1} \objex{pai1}-le \objex{wo3} \objex{liang3} \objex{xia4}.\\
    he pat-\textsc{pfv} I two \textsc{clf}\\
    \glt `He patted me twice.'
\z
\z

\ea\label{ex:redup-num}
  \ea[]{\gll \objex{ta1} \obj{pai1}-\obj{le}-\obj{yi}-\obj{pai1} \objex{wo3}.\\
   he pat-\textsc{pfv}-one-pat I\\
   \glt `He patted me a little bit.'}
   \ex[*]{\gll \objex{ta1} \obj{pai1}-\obj{le}-\obj{liang3}-\obj{pai1} \objex{wo3}.\\
   he pat-\textsc{pfv}-two-pat I\\}
\z
\z

Third, idioms (\ref{ex:idiom}) lose their idiomatic meaning when used with verbal classifiers (\ref{ex:clf-idiom}), but maintain their idiomatic meaning with reduplications (\ref{ex:redup-idiom}) \citep[230--231]{YangWei2017}.\footnote{
One reviewer suggests that the loss of the idiomatic meaning in (\ref{ex:clf-idiom}) but not in (\ref{ex:redup-idiom}) may be attributed to the use of the numeral \obj{san1} `three' in (\ref{ex:clf-idiom}),
because if \obj{san1} \obj{xia3} `three times' is replaced with \objex{yi2} \obj{xia4} `once' in (\ref{ex:clf-idiom}), he/she can still get the idiomatic interpretation.
We suggest that it is not \obj{san1} \obj{xia4} `three times' that is special, 
but it is \obj{yi2} \obj{xia4} `once' that is special.
We can replace \obj{san1} `three' with any number above two,
and the distinction still exist.
But \obj{yi2} \obj{xia4} `once' has acquired a duration reading `for a little while' that is not available to the other event quantifiers formed by \obj{xia4}, which only have the `for X times' interpretation (\citealt[77]{Deng2013}, \citealt[16]{Zhang2000}).
We think \obj{liang3} \obj{xia4} `twice' is following this tendency, too.
In this case, it is easy to interpret \obj{yi1} \obj{xia4} and \obj{liang3} \obj{xia4} not as referring to the actual number of action taking place,
but as duration adverbials as a whole,
thus differing them from ``actual'' verbal classifier phrases with other numerals.
}

\ea
  \ea\label{ex:idiom}
  \gll \objex{bao4} \objex{fo2}-\objex{jiao3}\\
  clasp Buddha-foot\\
   \glt Literal: `clasp the Buddha's foot'\\
   Idiomatic: `make a last-minute effort'

   \ex\label{ex:clf-idiom}
   \gll \objex{ta1} \objex{kao3shi4} \objex{qian2} \objex{bao4}-le \objex{san3} \objex{xia4} \objex{fo2}-\objex{jiao3}.\\
   he exam before clasp-\textsc{pfv} three \textsc{clf} Buddha-foot\\
   \glt `He clasped the Buddha's foot three times before the exam.' (idiomatic reading unavailable)

   \ex\label{ex:redup-idiom}
   \gll \objex{ta1} \objex{kao3shi4} \objex{qian2} \obj{bao4}-\obj{le}-\obj{bao4} \objex{fo2}-\objex{jiao3}.\\
   he exam before clasp-\textsc{pfv}-clasp Buddha-foot\\
   \glt Literal: `He clasped the Buddha's foot a little bit before the exam.'\\
   Idiomatic: `He made a bit of a last-minute effort before the exam.'
\z
\z

@@

%%%%%%%%%%%
\subsection{The reduplicant as an aspect modifier}\label{sec:asp}

A number of studies consider the reduplication to be an element that modifies the aspectual properties of the base verb \citep{Arcodiaetal2014, BascianoMelloni2017, YangWei2017} 
due to the delimitative aspectual meaning of reduplication. 
\citet{Travis1999, Travis2000} also analyzes the reduplication in Tagalog as an imperfective aspect marker.

@@

 \citet{Arcodiaetal2014} and \citet{BascianoMelloni2017} analyze the reduplication within the
framework of First Phase Syntax \citep{Ramchand2008}.
\citet{Ramchand2008} propose that an event is comprised of the following phrases: 
the causative subevent (\textit{init}P), the process subevent (\textit{proc}P) and the result subevent (\textit{res}P), which are ordered hierarchically, as illustrated in \figref{tree:ramchand}.\footnote{
The present study does not argue for a {NP} or a {DP} analysis and simply takes over the illustration provided in the cited papers.}
Dynamic and volitional verbs have the features [init proc] and are therefore located under \textit{init} and \textit{proc}  \citetext{\citealp[24]{Arcodiaetal2014}; \citealp[147]{BascianoMelloni2017}}.  
Achievement verbs possess the feature [res] and reside under \textit{res}  \citetext{\citealp[24]{Arcodiaetal2014}; \citealp[147]{BascianoMelloni2017}}. 
Stative verbs do not contain a \textit{proc}P \citep[152]{BascianoMelloni2017}.

@@

\citet{Arcodiaetal2014} and \citet{BascianoMelloni2017} assumed that the first element in the reduplication is the actual verb, which resides under \textit{init} and \textit{proc}, 
and that the second element is the copy of the verb, which resides in the complement position of \textit{proc} and serves as an event delimiter.
Since the second element occupies the same syntactic position as \textit{res}P, it should have complementary distribution with \textit{res}P
and should thus be incompatible with achievement verbs because of their [res] feature.
Furthermore, if \textit{proc}P does not exist in the event, as in the case of states, there should be no place for the reduplication either.

@@

 \citet[229]{YangWei2017} endorse the analysis of  reduplication as an aspect marker following the structure of Mandarin Chinese aspects proposed by \citet{Tsai2008}.
 \citet{Tsai2008} provides the syntactic analysis for aspect markers in Mandarin Chinese as shown in \figref{tree:tsai}.\footnote{Asp = Aspect}
He observed that  \obj{zhe} `\textsc{prog}', \obj{le} `\textsc{pfv}' and \obj{wan2} `\textsc{compl}' necessarily occur with additional information about the event denoted by the sentence (\ref{ex:incomplete}), 
while \obj{zai4} `\textsc{dur}' and \obj{guo4} `\textsc{exp}' can occur without further information (\ref{ex:complete}).

\ea\label{ex:incomplete}
 \gll \objex{Xiao3li3} \objex{chi1}-zhe/le/\objex{wan4} fan *(le).\\
 Xiaoli eat-\textsc{prog}/\textsc{pfv}/\textsc{compl} meal \textsc{ptc}\\
 \glt `Xiaoli is eating/ate/finished eating the meal.'
\z

\ea\label{ex:complete}
\gll \objex{Xiao3li3} (\objex{gang1cai2}) \objex{zai4} \objex{ku1}/\objex{ku1}-\objex{guo4}.\\
Xiaoli just.now \textsc{dur} cry/cry-\textsc{exp}\\
\glt `Xiaoli was crying/cried just now.'
\z
He thus proposed three aspect positions under TP. \textit{zai} and \textit{guo} reside under Asp$_1$, while \textit{zhe} and \textit{le} under Asp$_2$, as illustrated in \figref{tree:tsai}.\footnote{\citet{Tsai2008} differentiated the middle and the inner aspect based on the fact that \obj{wan2} can only occur with certain types of predicate. This differentiation does not play a role for our purpose and will not be further discussed here.}

@@

\ea\label{ex:redup-tsai}
\ea[*] {\gll \objex{ta1} \obj{xiao4}-\obj{xiao}\\
he laugh-laugh\\}
\ex[] {\gll \objex{ta1} \obj{xiao4}-\obj{le}-\obj{xiao4}\\
he laugh-\textsc{pfv}-laugh\\
\glt `He laughed a little.'}
\ex[] {\gll \objex{ta1} \obj{xiao4}-\obj{xiao}, \objex{bu4} \objex{shuo1hua4}\\
he laugh-laugh not speak\\
\glt `He laughed a little, and didn't speak.'}\label{ex:redup-tsai-co}
\z
\z

@@

This analysis would result in a mismatch between syntax and semantics. 
Even though \obj{le}, \obj{guo4} and reduplication all mark perfective aspects (\sectref{sec:aspM}, \citealt{Dai1997, XiaoMcEnery2004}),
\obj{guo4} is situated under Asp$_1$ while \obj{le} and the reduplication are under Asp$_2$, as can be seen from \figref{tree:redupasp}.

In sum, both analyses of the reduplicant as an aspect modifier do not seem to be convincing.

@@

%The following section discusses previous literature which proposed a special construction for the reduplication.

@@

\citet*{FanSongBond2015} provide a unified HPSG analysis for the reduplication of both verbs and adjectives in Mandarin Chinese.
They consider reduplication to be a morphological process and modeled it via lexical rules.
They provide the lexical rule (\ref{avm:fsb-redup}) for reduplication in general,
and further propose \type{redup-a-lr} and \type{redup-v-lr} as subtypes of \type{redup-type}, 
as illustrated in (\ref{avm:fsb-redup-a}) and (\ref{avm:fsb-redup-v}) respectively.\footnote{%
  Note that the format in which the lexical rule is given is not the input--output format usually
  used for lexical rules in HPSG. Instead it is depicted as a unary branching phrase structure
  rule: the input is the daughter on the right-hand side of the rule. The output is the mother on
  the left-hand side. The view of lexical rules as unary branching rules is adopted in most current work on
  lexical rules \citep{BC99a,Meurers2001a} despite the notation that is commonly assumed.  
}
For them, the reduplication functions as an intensifier predicate, as represented in the \textsc{predicate (pred)} in the \textsc{constructional-content (c-cont)}.
The \type{intensifier\_x\_rel} has two subtypes: \type{redup\_up\_x\_rel} for the amplifiying meaning of adjectival reduplication and \type{redup\_down\_x\_rel} for the delimitative meaning of verbal reduplication.
The orthography is handled separately.
The AABB form for adjectives and the ABAB form for verbs, as well as the AAB form for V-O compounds, are handled as irregular derivation forms.

@@

This approach provides a unified account for adjectival and verbal reduplication.
Their commonalities are captured by inheritance hierarchies of the intensifier predicates and the lexical rules.
In the case of verbal reduplication, A-\textit{yi}-A is analyzed as an alternative orthographical form of AA.
This correctly captured the intuition that AA and A-\textit{yi}-A express the same meaning and only differ from each other phonologically/orthographically (see \sectref{sec:core-sem}).
